Regime transition identification for water governance at a basin scale

### 2020-11-23 tex/main/manuscript.tex
polish througtout by Wei's comments

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
\label{significance}
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	It is a well-known fact that development of human societies backs on water use.
	Therefore, as natural water cycle has been dominated by growing socio-economic processes, big river basins are roundly governed stage by stage for further water use. 
	We propose a new method with an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
	Since our index integrates various dimensions of water governance (who gets what water, when and how), a widespread regime transition schema can be summarized after then. 
	By identifying governance challenges, the schema can be a useful guideline for basins all around the world in their sustainability. 
}

@@

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and triggered various regime shifts at a basin scale all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how much, identification for its changes is critical to guiding efficient and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, combining three main dimensions of water governance (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts.
	% 将该指数应用于中国黄河流域，可以看出，在过去半个多世纪中，有三个政权的转变是由经济增长、管理和效率提高引起的。  
	By applying this index to a typical fast-changing basin -the Yellow River Basin, China, it paints shifts between three water governance regimes throughout half a century, which were caused by environmental, economic social and political changes.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on these, we summarized a widespread transition schema of water governance regime, paralleled with the transformative trajectory towards hydro-social water cycle.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since different governance challenges mainly occurred at different stages in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}

@@

\label{introduction-section-1}
% 水资源在人类世的重要性，是支持人类社会发展的基础。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for Earth system processes, but also supporting development of human societies. 
%* add references
% 然而，根据人类用水的需求，人类的改造对自然水循环产生了深远的影响，并将其发展轨迹逐步推向了水社会循环。
Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% 面对人类世世的重大转变，世界许多大河流域，也是经济和文明的热点地区，迫切需要成功的治理以实现可持续发展
Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful governance for Sustainability
\cite{bestAnthropogenicStressesWorld2019}. 
% 作为地球系统治理框架的一个组成部分，水治理需要对人类社会和水资源利用之间的复杂关系有深刻的理解。
As an integral part of a proposed Earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
% Biermann et al., 2012.
% 因此在流域尺度上，识别由向水-社会水循环的转变所引起的变化是至关重要的。
Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.

\label{introduction-section-2}
% 缺乏治理就是缺乏可持续性
Missing governance means missing sustainability.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used? (supply)'', ``How to balances different water use services? (purpose)'' and ``How to allocate water equally and efficiently? (allocation)''.
% Regime 和 Regime shift 的定义。
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 因此，确定关于水治理的制度变化是重要的，它标志着水资源利用的实质性变化，并导致可持续性方面的新的治理挑战。
Identification of regime shifts regarding water governance, therefore, is important as a signal of substantive change in water use and lead to new challenges to sustainability.
% 随着环境、经济、社会和政策情况。
Along with environmental, economic, social and political changes, the three dimensions may compose various water governance regimes. 
% 首先，受环境恶化和经济发展用水的影响，水资源短缺会增加社会的压力，但水库建设等管理政策有助于缓解压力。
Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but governance policies (such as construction of reservoirs) can be helpful
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of considerations through water governance
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
% 总的来说，用水治理决定了与用水的“压力”、“供给”和“分配”，而三者在用水转向社会-水循环的过程中都发生着不断的变化
Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation), and the lack of simple but comprehensive ways to identify regime shifts leaves crucial gaps towards successful governance (Figure~\ref{fig:framework}).

\label{introduction-section-3}
% 黄河流域(YRB，见\textit{ Appendix}方法S1)，在中国经历了最激烈的水资源开发和最剧烈的管理制度变化。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges to water governance since the ancient time.
% 对1960年以前的中国，黄河巨大的含沙量不仅给YRB带来了洪泛灾害，更为利水带来巨大困难。
Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
% 随着水保措施、水库调水调沙、修堤等治理措施的落实才得到了有效遏制。
Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
% 但随之而来的是越来越严重的断流，为水治理带来了新的挑战。 
However, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies to deal with.
% 如今，黄河流域仍面临严峻的治理挑战，因为区域的用水需求仍很难被全盘满足，而必须做出权衡。
Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
% 总之，随着人类影响逐步加大，为了应对层出不穷的治理挑战，黄河流域水治理发生的迅猛转变堪称世界之最。
All in all, the YRB has been the most rapid-changing basins in the world with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
% 因此如果能理解黄河水治理稳态的转换过程，其模式能为世界大河流域用水的可持续提供见解。
Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.

\label{introduction-section-3}
% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, based on three key dimensions of water governance, we develop an Integrated Water Governance Index (IWGI) to indicate changes of water governance at a basin scale (Figure~\ref{fig:framework}).
% 使用案例研究
Then, by applying it to the YRB, we analysed regimes shifts of water governance and their main causes.
% 最后总结出一般性框架
Finally, we summarized a general regime transition schema which can be a useful guideline for basins to develop in a coordinated way, with echoes to the different kinds of challenges regarding water governance.

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details). Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis. (1) supply shifts between scarcity of water resources and abundance of water resources, which means there is shortage of water supply or not. (2) purpose of water can move between provisioning services or non-provisioning services, indicating how much water were used in food supporting. (3) allocation can move between balanced or lopsided, when allocation of water resources between different sectors or regions changed. We presume that water governance regimes equally weighted by these basic dimensions, whose combination can highly relate to basin development. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the changes after combining the three dimensions. Because the above three dimensions are changing with the trajectory towards hydro-social water cycle, their combined water governance status is also different. When abrupt change occur during this process, they may indicate a regime shift in water governance, and we propose an indicator to monitor this change.
	}
	\label{fig:framework}
\end{figure*}

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use density (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply. These marked reservoirs, therefore are significant for the entire basin, far crucial than regional development.
		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2). Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order.
	}
	\label{fig:Causes}
\end{figure}

@@

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. There is a transformation towards the hydro-social water cycle where red loop increases.
		\textbf{A. Natural phase:} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent. Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore. 
		Water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
	}
	\label{fig:summary}
\end{figure*}

>>>>

% Please add a significance statement to explain the relevance of your work
% PNAS特有的“Significance陈述”，用不超过120个字来说明研究的意义和亮点
\significancestatement{
\label{significance}
	% Authors must submit a 120-word maximum statement about the significance of their research paper written at a level understandable to an undergraduate educated scientist outside their field of speciality. The primary goal of the significance statement is to explain the relevance of the work in broad context to a broad readership. The significance statement appears in the paper itself and is required for all research papers.
	It is a well-known fact that development of human societies backs on water use.
	Therefore, as natural water cycle has been dominated by growing socio-economic processes towards a hydro-social water cycle, big river basins are roundly governed stage by stage for further water use. 
	We propose an integrated index to detect water governance regimes and applying it to the Yellow River Basin, a typical fast-changing basin in China.
	Three water governance regimes are identified (massive supply regime, purpose turned regime, all-sided governance regime) and a widespread regime-transition schema can be summarized after then. 
	By linking the transition with major water governance challenges, the schema can be a useful guideline for big river basins all around the world in their sustainability. 
}

@@

%tag 摘要
% 为了
\begin{abstract}
	\label{abstract}
	% 为了持续的社会经济发展，人类治理了大型河流，并在世界范围内引发了一系列流域尺度的稳态转换。
	For water uses in sustaining socio-economic development, human have governed large rivers and led a transformation towards a hydro-social water cycle within basins all around the world. 
	% 由于水治理制度决定谁、何时和如何获得水，因此确定其过渡对于指导有效和可持续的用水至关重要。
	Since water governance regime decides who gets what water, when and how much, identification for its changes is critical to guiding efficient and sustainable water uses.
	% 在这里，考虑到水治理的三个主要维度(压力、供应和分配)，我们开发了一个流域尺度上的综合水治理指数(IWGI)，以检测制度的变化。
	Here, combining three main dimensions (supply, purpose and allocation), we develop an Integrated Water Governance Index (IWGI) at a basin scale to detect regime shifts of water governance.
	% 将该指数应用于典型的快速变化的流域——中国黄河流域，描绘了由环境、经济、社会和政治变化引起的长达半个世纪的三种水治理制度(大规模供应制度、目的性转向制度、全方位治理制度)之间的变迁。
	By applying the index to a typical rapid-changing basin -the Yellow River Basin, China, shifts between three water governance regimes (massive supply regime, purpose turned regime, all-sided governance regime) throughout half a century are well painted, which were caused by environmental, economic social and political changes.
	% 在此基础上，我们总结了一个与水社会循环相对应的一般制度变迁模式。
	Based on that, we summarize a widespread transition schema of water governance regime, paralleled with a transformative trajectory towards hydro-social water cycle in the Anthropocene.
	% 由于资源挑战和结构挑战主要困扰不同制度下的水治理，这一过渡模式可以作为协调大流域治理的有益指导。
	Since different governance challenges mainly occurred at different stages in transition, this schema can be a useful guideline for governing big river basins in a coordinated way.
\end{abstract}

@@

\label{introduction-section-1}
% 作为“人类世行星戏剧的中心”, water 不仅对地球系统进程至关重要，而且还支持着人类社会的发展。
\dropcap{W}ater, at “the centre of the planetary drama of the Anthropocene”, is not only essential for earth system processes, but also supporting development of human societies. 
%* add references
% 由于人类对水的依赖，人类活动深刻地改变了自然水循环，并逐步走向水-社会水循环。
Because of relying on water use, human activities have profoundly modified the natural water cycle and led the trajectory towards a hydro-social water cycle stage by stage
\cite{gleesonIlluminatingWaterCycle2020,cummingLinkingEconomicGrowth2018}.
% 面对这一重大转型，世界上许多大流域作为经济和文明热点，迫切需要成功的可持续治理
Facing this major transformation, many of the world's big river basins, also hot spots of economy and civilization, are urgently in need of successful water governance for sustainability
\cite{bestAnthropogenicStressesWorld2019}. 
% 水治理作为地球系统治理框架的重要组成部分，需要对人与水之间复杂的关系有深刻的理解。
As an integral part of a proposed earth system governance framework, water governance requires deep understanding of the complex relationships between human and water.
% Biermann et al., 2012.
% 因此，识别流域尺度上由水-社会水循环转变引起的水治理变化至关重要。
Therefore, it is crucial to identify changes of water governance induced by the transformation towards hydro-social water cycle, at a basin scale.

\label{introduction-section-2}
% 缺乏治理就是缺乏可持续性
Missing governance means missing sustainability.
% 根据联合国开发计划署(UNDP)的说法，水管理决定了用水的三个关键方面:“有多少水可供使用?、“如何平衡用水服务?”“以及‘如何平等有效地分配水资源?’”
According to United Nations Development Programme (UNDP), three key dimensions are decided by water governance regime directly (see \textit{SI Appendix} Methods S1): ``How much water can be used? (supply)'', ``How to balances different water use services? (purpose)'' and ``How to allocate water equally and efficiently? (allocation)''.
% 制度是系统结构和功能的一种稳定状态，其大规模的持续变化可能对系统结果产生实质性的影响，具有广泛的级联效应，即制度变迁.
Regime is a stable state of system’s structure and function, of which large and persistent changes may lead to substantive impacts on the outcomes of system with widespread cascading effects, defined as regime shifts 
\cite{rochaCascadingRegimeShifts2018,schefferCatastrophicRegimeShifts2003, schefferCatastrophicShiftsEcosystems2001}.
% 因此，制度的转变是水治理发生实质性变化的信号，可能导致对可持续性的新挑战。
Regime shifts, therefore, is a signal of substantive change of water governance and may lead to new challenges to sustainability.
% 然而，随着环境、经济、社会和政治方面的变革，水治理制度可以从上述每一个关键方面(供应、目的和分配)发生重大变化。
Along with environmental, economic, social and political changes, however, water governance regimes can substantially shift from each of the above key dimensions (supply, purpose, and allocation).
% 首先，受环境恶化和进一步经济增长对水的需求的影响，维持社会的水供应可能会因为缺水而面临压力，但治理政策(如修建水库)可能会有所帮助.
Firstly, effected by environment deteriorate and water demands of further economic growth, maintaining water supply for societies can face stress because of scarcity, but policies (such as construction of reservoirs and channels) can be helpful
\cite{postelHumanAppropriationRenewable1996, greveGlobalAssessmentWater2018, qinFlexibilityIntensityGlobal2019}.
% 其次，在供应用水(如家庭用水和粮食生产用水)和非供应用水(如工业生产或能源用水)之间存在权衡，这需要由治理制度来平衡。
Secondly, there is trade-off between provisioning-purpose water use (such as domestic use and food production uses) and non-provisioning-purpose water (such as uses for industrial production or energy), which in need of weights through water governance
\cite{liuWaterScarcityAssessments2017, florkeWaterCompetitionCities2018}.
% 第三，由于配置是流域关注的问题，它不仅受到区域环境基础的影响，而且还受到区域经济比较优势的影响，而经济比较优势可能受到社会发展和政策的影响。
Thirdly, since governance concerns water allocation at the whole basin, it not only influenced by regional environmental context, but also by regions' economic comparative advantages, which is easily altered by social and political changes.
% 综上所述，随着向以人为主导的水-社会水循环的转变，水治理制度由三个变化的维度(供应、目的和分配)决定，缺乏简单而全面的方法来确定制度变化，这对成功治理留下了关键的差距.
Taken together, along with the transformation towards a human-dominated hydro-social water cycle, water governance regimes are determined by three changing dimensions (supply, purpose and allocation). However, the lack of simple but comprehensive method to identify changes of water governance regime leaves fatal gaps towards successful water governance for sustainability (Figure~\ref{fig:framework}).

\label{introduction-section-3}
% 黄河流域(YRB，详见方法S2)经历了中国最密集的用水和剧烈的制度变迁，从古代起就面临着水资源管理方面的非凡挑战。
The Yellow River Basin (YRB, see \textit{Appendix} Methods S2 for details) had experienced the most intense water use and dramatic shifts of regime in China, with extraordinary challenges in water governance from the ancient time.
% 半个世纪前，黄河巨大的泥沙负荷不仅给黄河带来了灾难，也给黄河的用水带来了困难。
Half century ago, the huge sediment loads of the Yellow River not only brought disasters, but also made it difficult for water use. 
% 自20世纪60年代以来，通过实施养护措施、水库调蓄和堤防工程，这些问题得到了有效遏制。
Since 1960s, with implementations of conservation measures, regulation reservoirs, and levees constructions, these issues were effectively contained.
% 然而，由于过度用水，黄河的严重干涸带来了新的治理挑战，并推动了一系列相关政策(如调节用水和限制取水)来应对。
However, because of over water use, serious drying up of the Yellow River led new governance challenges and promoted a range of related policies (such as regulating water use and limiting water withdrawals) to deal with.
% 今天，由于水的需求仍然难以完全满足，各区域和部门之间必须进行各种权衡，要取得成功的水治理还有很长的路要走。
Today, as water demands are still difficult to be completely met and various trade-offs must be involved between regions and sectors, there is still a long way towards successful water governance.
% 总而言之，YRB是世界上变化最迅速的盆地，对由环境、经济、社会或政治因素引起的无休止的治理挑战作出各种各样的反应。
All in all, the YRB has been the most rapid-changing basins in the world, with myriad responses to the endless governance challenges induced by environmental, economic, social or political factors.
% 因此，确定YRB内的水管理制度变化可以为世界快速变化的大河流流域提供洞察，以应对可持续发展方面的挑战。
Therefore, identifying the regime shifts for water governance within YRB can provide insights to the world's rapid-changing big river basins for meeting challenges towards sustainability.

\label{introduction-section-3}
% tag 引言最后一段
% 这里我们整合了三个方向，提出了描绘流域人水关系的指数
Here, based on three key dimensions (supply, purpose and allocation) of water governance, we develop an Integrated Water Governance Index (IWGI) to detect changes of water governance at a basin scale (Figure~\ref{fig:framework}).
% 使用案例研究
By applying the index to a typical rapid-changing big river basin (the YRB), we analysed the complicated regimes shifts of water governance and their main causes in a comprehensive but simple way.
% 最后总结出一般性框架
Finally, a general regime transition schema is summarized, which can be a practicable guideline for big river basins to governance in a coordinated way towards sustainability since it reveals widespread challenges regarding water governance.

\begin{figure*}%[htbp]
	\centering
	\includegraphics[width=0.8\linewidth]{../../figures/main/framework.jpg}
	\caption{
		A framework for understanding the relationship between transformation towards hydro-social cycle and water governance regimes, with a main goal in detecting regime shifts by a simple and comprehensive index.
		% 图A是水资源利用的三个维度。每个维度都有两个极点（红色字表示），指示水资源利用在该轴上的两个变化方向。
		\textbf{A,} three key dimensions (supply, purpose and allocation) of water governance (see \textit{Appendix SI} Methods S4 for details). Each dimension has two poles (denoted in red) which indicate the two potential directions of changes along that axis: (1) ``supply'' shifts between scarcity and abundance. (2) ``purpose'' weighted between provisioning services or non-provisioning services. (3) ``allocation'' changes between balanced or lopsided. We presume that water governance regimes equally weighted by these basic dimensions. 
		% 图B是将三个维度结合后的变化情况。因上述三个维度随着社会发展而不断变化，其组合的水资源利用状态也不同。这个过程中当突变发生时，可能标志着水资源利用发生了稳态转换，因此我们需要一个指标来监测其变化。
		\textbf{B,} the governance changes combined the three dimensions. Because the above three dimensions change along with the trajectory towards hydro-social water cycle, combined water governance status is also various with that. When abrupt change occurs during this process, it may indicate a regime shift in water governance.
	}
	\label{fig:framework}
\end{figure*}

@@

\begin{figure}[th!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/causes.pdf}
	\caption{
		Causes of water governance regime shifts: environment changes, economic growths and efficiency changes, social transformation and water governance policies.
		\textbf{A.} Changes of total irrigated area, and water consumptions in per unit of area (\textit{SI Method} S2).
		\textbf{B.} Changes of gross values added (GVA) of industry and services, and their water use intensity for unit production (WUI) respectively (\textit{SI Appendix} Method S2).
		\textbf{C.} Completed time of each new reservoir and their located regions' water use percentages in basin's total water use (WU), at that time. Red ones denote hub reservoirs in the basin, which plays a role in basinal integrated water management. Size of the points indicates their magnitude of water storage capacities. Some important or special reservoirs' name denoted: (1) Xiaolangdi reservoir and Sanmen Reservoir were constructed mainly responsible for managing sediments of the Yellow River. (2) Liujia Gorge, Longyang Gorge, were constructed mainly responsible for managing water flood discharge and water supply. These marked reservoirs, therefore are more significant for the entire basin, rather than regional development.
		\textbf{D.} Social transformations and national levels' policies related to water governance (see \textit{Appendix SI} Table S2). Four transformations are ``ethos of conquer nature (since 1958)'', ``reform and opening-up (since 1978)'', ``the 87 Water Diversion Scheme (since 1987)'', ``environmental regulation (since 2003)'' in order.
	}
	\label{fig:Causes}
\end{figure}

@@

\begin{figure*}[htbp!]
	\centering
	\includegraphics[width=\linewidth]{../../figures/main/transition.jpg}
	\caption{
		\textbf{Transition schema of water governance.} Blue pathways dominated by natural water loop while red ones dominated by socio-economic loops. There is a transformation towards the hydro-social water cycle where red loop increases.
		\textbf{A. Natural phase:} As an indispensable provisioning-purpose resource, the main functions of water resource is to support crop, livestocks and human-beings, which are the basic ecological services.
		\textbf{B. Local phase:} With local socio-economic systems developing, industry and services (also known as the secondary and the tertiary industry) calling for further water consumptions. What's more, better organized socio-economic system and developed technology gives humans abilities in better managing water resources, with intensive intervention in the natural water cycle. 
		\textbf{C. Regional phase:} With further developed and economically efficient industries and services, trade-off between provisioning-purpose and non-provisioning-purpose water use becomes prominent. Rather than determined by local socio-economic systems any more, water withdrawals and management act as considerations within the entire basin more, therefore. 
		\textbf{D. Water governance challenges} Throughout the transition regimes, water governance faces primarily economic and environmental challenges in the early stages while social and policy challenges in the later stages.
	}
	\label{fig:summary}
\end{figure*}
